---
title: "Demo - Exponential Smoothing & Colombian Coffee"
author: "Adam L. Seale"
date: "May 9, 2018"
output: pdf_document
---

```{r echo=F, message=F, error=F, warning=F}
setwd("../")
invisible(library(dplyr))
library(forecast)
invisible(source("load_combined_data.R"))
```

As an example of basic time-series smoothing and forecasting, let's create a double exponential smoothing model for the amount of consumer-available coffee in Colombia. We'll specify our model as AAN: additive error, additive trend, and no cyclical factors - then visualize it as follows:

```{r}
colombian_data <- food_per_capita %>% filter(Area == "Colombia")
coffee <- colombian_data$Coffee
model <- ets(coffee, "AAN")
plot(predict(model),
     main = "Coffee Availability Forecast - 80% and 95% Likeliood Ranges",
     xlab = "Years since 1960",
     ylab = "Relative Available Amount")
```

A reasonable interpretation of this graph might be:

"It is 80% likely that the amount of available coffee in Colombia in 2014 - knowing only values prior to that - will not increase or decrease by more than about half its present value."

This admittedly isn't an *enormously* valuable insight; however, I do hope it serves to demonstrate proficiency.